---
output: github_document
---

```{r setup, echo = FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(flextable)
library(ftExtra)
library(scales)
library(reactable)
library(reactablefmtr)
library(RCurl)
library(htmltools)
library(crosstalk)
library(ggridges)

pbp_data_bdb <- read.csv("data/plays.csv") %>% 
  mutate(uId = paste(gameId,playId,sep = "_"))

tackle_list <- readRDS("data/tackles_info_data_full_oos2.rds")

tackles <- tackle_list[[1]]
tackle_info_real2 <- tackle_list[[2]]
tackle_info_simple2 <- tackle_list[[3]]
tackle_pred_real <- tackle_list[[4]]
tackle_pred_s <- tackle_list[[5]]
tackle_vals <- tackle_list[[6]] 
best_tacklers <- tackle_list[[7]]

```


# PEP: A metric for evaluating tackles

This is the github repository for the corresponding submission to the NFL Big Data Bowl 2024 competition on Kaggle. The full notebook can be viewed [here](https://www.kaggle.com/code/robbwu/pep-a-metric-for-evaluating-tackles).

## Quick Summary

In this contribution, we developed the metric PEP for quantifying the value of tackles. It allows practitioners to assess players, particularly in terms of their tackling abilities. Our approach allows for within-play conditional density estimation of the end-of-play yard line which serves as a basis for the evaluation of tackle performance measured by prevented expected points by artificially removing the tackler from the data. Importantly, our method incorporates distributional information, i.e., heteroscedasticity and multimodality, which would be lost when solely relying on point predictions. Therefore, the uncertainty can propagate to the level of expected points, leading to an accurate quantification of expected points prevented by the tackle.

```{r animation, fig.show='animate', ffmpeg.format='gif', dev='jpeg', echo = FALSE,fig.width= 8,fig.height=8,fig.align='center',interval = 0.4}
library(scales)

coldens = "#009E73"
collos = "#CC79A7"
coleop = "#999999"
coloff = "#0072B2"
coldef = "#D55E00"

ex_play <- readRDS("data/example_play_for_anim3.rds")
gpId <- ex_play[[1]]
tracking_play <- ex_play[[2]]
play_train <- ex_play[[3]]
pred <- ex_play[[4]]
pbp_info <- ex_play[[5]]


par(mfrow = c(2,1), oma = c(5,4,0,0) + 0.1, mar = c(0, 0, 0, 2) + 0.1)
for(i in 1:(nrow(pred)-7)){
  plot(tracking_play$x_bc[i], tracking_play$y_bc[i], pch = 1, lwd = 6, col = coloff, 
       xlim = c(0,min(round(max(tracking_play$x_bc),-1)+30,100)), ylim = c(-53.3/2, 53.3/2+5), 
       xlab = "", ylab = "", bty = "n",xaxt = "n", yaxt = "n")
  text(x=min(round(max(tracking_play$x_bc),-1)+30,100)/2, y=53.3/2+2.5, pbp_info$desc, cex=.7)
  segments(x0 = 1:20 *5,
           y0 = 53.3/2,
           x1 = 1:20 *5,
           y1 = -53.3/2,
           col = "lightgray", lwd = 0.5)
  segments(x0 = c(0,0),
           y0 = c(53.3/2,-53.3/2),
           x1 = c(100,100),
           y1 = c(53.3/2,-53.3/2),
           lwd = 1.5)
  
  segments(x0 = pbp_info$yardline_100,
           y0 = 53.3/2,
           x1 = pbp_info$yardline_100,
           y1 = -53.3/2,
           col = collos,lty = 2)
  #abline(v = tackle_info$yardline_100, col = collos,lty = 2) # line of scrimmage
  
  segments(x0 = 0,
           y0 = 53.3/2,
           x1 = 0,
           y1 = -53.3/2,
           lwd = 1.5)
  #abline(v = 0, lwd = 1.5) # endzone
  
  segments(x0 = pbp_info$true_yardline,
           y0 = 53.3/2,
           x1 = pbp_info$true_yardline,
           y1 = -53.3/2,
           col = coleop,lty = 2)
  
  # plot predicted yard end yard line
  for(j in 1:1000){
    segments(x0 = max(tracking_play$x_bc[i]-pred[i,j],0),
             y0 = 53.3/2,
             x1 = max(tracking_play$x_bc[i]-pred[i,j],0),
             y1 = -53.3/2,
             lwd = 2, col = alpha(coldens, 0.01))
    #abline(v = tackle_frame$x_bc-pred_r[j], lwd = 2, col = alpha(coldens, 0.01))
  }
  segments(x0 = max(tracking_play$x_bc[i] - mean(pred[i,]),0),
           y0 = 53.3/2,
           x1 = max(tracking_play$x_bc[i] - mean(pred[i,]),0),
           y1 = -53.3/2,
           col = 1, lwd = 2)
  #abline(v = tackle_frame$x_bc - mean(pred_r), col = 1, lwd = 2) # expected eop yardline
  segments(x0 = max(tracking_play$x_bc[i] - mean(pred[i,]),0),
           y0 = 53.3/2,
           x1 = max(tracking_play$x_bc[i] - mean(pred[i,]),0),
           y1 = -53.3/2,
           col = coldens, lwd = 1)
  #abline(v = tackle_frame$x_bc - mean(pred_r), col = coldens, lwd = 1) # expected eop yardline
  
  points(tracking_play$x_bc[i], tracking_play$y_bc[i], pch = 1, lwd = 6, col = coloff)
  points(tracking_play$x_bc[i], tracking_play$y_bc[i], pch = 16, col = coloff)
  
  for(j in 2:11){
    points(tracking_play[i,paste0("x_or_off", j)], tracking_play[i, paste0("y_or_off", j)], pch = 20, col = coloff)
  }
  for(j in 1:11){
    points(tracking_play[i,paste0("x_or_def", j)], tracking_play[i, paste0("y_or_def", j)], pch = 20, col = coldef)
  }
  points(tracking_play$x_football[i], tracking_play$y_football[i], pch = 9, col = "coral1", lwd = 2)
  legend(x = pbp_info$yardline_100-10, y = -16,
         legend = c("Off","Def","Football","LOS","EOP"),
         col = c(coloff,coldef,"coral1",collos,coleop),
         pch = c(20,20,9,NA,NA), lty = c(NA,NA,NA,2,2),
         cex = 0.7, ncol = 2,bg = "white") 
  
  plot(density(pmax(tracking_play$x_bc[i]-pred[i,],0), bw = 2.5,from = 0), 
       col = coldens, lwd = 2, xlim = c(0,min(round(max(tracking_play$x_bc),-1)+30,100)), bty = "n", main = "", xlab = "eop yardline")
  abline(v = 1:20 *5, col = "lightgray", lwd = 0.5)
  abline(v = pbp_info$yardline_100, col = collos,lty = 2)
  abline(v = 0, lwd = 1.5) # endzone
  abline(v = max(tracking_play$x_bc[i] - mean(pred[i,]),0), col = 1, lwd = 2)
  abline(v = max(tracking_play$x_bc[i] - mean(pred[i,]),0), col = coldens, lwd = 1)
  abline(v = pbp_info$true_yardline, col = coleop,lty = 2)
  
  #Sys.sleep(0.1)
}

```

## Code Information

In the `prg` directory all necessary code to reproduce our work is found. Due to size restriction, we are not able to upload our random forest model for the conditional density estimation. The necessary scripts for the random forest are the `preprocessing_new.R` and the `train_eop_model_new.R` files. To calculate our PEP metric, the ep model uploaded in the `models` folder can be used (the code from the `ep_models.R` script can also be used to create your own model). Finally, the `calc_tackle_value.R` file can be used to obtain PEP values for each tackle. 

